---
title: "Project3 Tutorial"
author: "Zhien Yu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Project3 Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Package Project 3 has 4 functions. 
1) "my_t.test", 2) "my_lm", 3)"my_knn_cv", 4)"my_rf_cv"
This package should be installed by code:
```{r, eval=FALSE}
devtools::install_github("YZhien/final", build_vignette = TRUE, build_opts = c())
```

```{r setup}
library(Project3)
```

```{r}
# get our data for my_t.test
lifeExp_num <- my_gapminder$lifeExp
# a test of hypothesis for H0 :u = 60
#                          H1 :u < 60
my_t.test(lifeExp_num, "less", 60)
```
Using a = 0.05, we successfuly reject the null hypothesis and accept the alternative hypothesis since p value is smaller than 0.05. Thus mean of life expectation is less than 60.

```{r}
# get our data for my_t.test
lifeExp_num <- my_gapminder$lifeExp
# a test of hypothesis for H0 :u = 60
#                          H1 :u > 60
my_t.test(lifeExp_num, "greater", 60)
```
Using a = 0.05, we fail to reject the null hypothesis since p value is larger than 0.05. Thus, Mean of life expectation is less than 60.

```{r}
# get our data for my_t.test
lifeExp_num <- my_gapminder$lifeExp
# a test of hypothesis for H0 :u  =  60
#                          H1 :u != 60
my_t.test(lifeExp_num, "two.sided", 60)
```
Using a = 0.05, we fail to reject the null hypothesis since p value is larger than 0.05. Thus, Mean of life expectation is less than 60.

